Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Matter Power Spectra

### 2025-06-30 paper/main.tex
specify data can be accessed via Github for reproducibility

The remainder of the paper is organized as follows.  Section \ref{sec:data} 
introduces our motivating application, the Mira-Titan simulation suite.  
Section \ref{sec:hm_fit} describes our hierarchical Bayesian DGP and 
validates its performance on synthetic exercises and the CAMB simulations.  
Leveraging this trained model, Section \ref{sec:pred} details 
our procedure for predicting at unobserved cosmologies, benchmarking against
state-of-the-art competitors on the CAMB and Mira-Titan simulations. 
Section \ref{sec:disc} concludes with a discussion of our contributions and avenues for 
future research.  We provide reproducible code and an {\sf R} package for our 
Bayesian DGP model in a public git repository.\footnote{\url{https://github.com/stevewalsh124/dgp.hm}}

@@

>>>>

The remainder of the paper is organized as follows.  Section \ref{sec:data} 
introduces our motivating application, the Mira-Titan simulation suite.  
Section \ref{sec:hm_fit} describes our hierarchical Bayesian DGP and 
validates its performance on synthetic exercises and the CAMB simulations.  
Leveraging this trained model, Section \ref{sec:pred} details 
our procedure for predicting at unobserved cosmologies, benchmarking against
state-of-the-art competitors on the CAMB and Mira-Titan simulations. 
Section \ref{sec:disc} concludes with a discussion of our contributions and avenues for 
future research.  We provide data and reproducible code and an {\sf R} package for our 
Bayesian DGP model in a public git repository.\footnote{\url{https://github.com/stevewalsh124/dgp.hm}}

@@

\section{Disclosure}
The authors report there are no competing interests to declare.
